New insights into the Weddell Sea ecosystem applying a network approach

### 2022-10-31 Manuscript/Manuscript.Rmd
Updating Results

In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions. The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 3, Table 1).

@@

Regarding the distribution of the species' mean interaction strength and its relationship with the unweighted properties, we found that interaction strength-trophic level showed the strongest linear regression: the higher the trophic level of the species, the higher its mean interaction strength. We also found a positive relationship with the degree (total number of interactions). On the other hand, CONTINUE HERE ...

>>>>

In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions. The distribution of the interaction strength best fit to a log-Normal model, meaning that there is a prevalent skew towards weaker interactions (Figure 3, Table 1).

@@

Regarding the distribution of the species' mean interaction strength and its relationship with the unweighted properties (Figure 4), we found that interaction strength-trophic level showed the strongest linear regression: the higher the trophic level of the species, the higher its mean interaction strength. We also found a positive relationship with the degree (total number of interactions). On the other hand, there was no evident relationship with trophic similarity. Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength, though "Demersal" and "Land-based" concentrated the majority of the species with relatively higher interaction strength. Species inhabiting the benthic realm showed the lowest mean interaction strength (Figure 4D).
